---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
  font-family: 'Nikolas'
}

p {
  font-size: 21px;
}

img {
  display: block;
  margin: 30px auto;
}

```

# Do the duration of phone session and purpose affect productivity?
This report investigates whether the duration of phone usage per sessions and purpose actually affects productivity. 

---

```{r}
# Read csv file
data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTJgZ7FE7aimKPdtwqmMt7mAlHHBf5Ar8rQsg31Ckf7YshOTYuTiw7mvg-_gG4XuxgYzUpomlBL2hjr/pub?gid=984475425&single=true&output=csv")

# Rename variable 
latest_data <- data %>%
  rename(minutes_per_session = 2,
         purpose = 3,
         productivity = 4)

```

## The Phone Use Purpose Affect on Productivity

```{r}
# Bar chart 
latest_data %>%
  ggplot() +
  geom_bar(aes(x = purpose, fill = productivity)) +
  labs(
    title = "Phone Usage Purpose and Productivity Impact",
    subtitle = "Comparing how different types of phone use affect productivity",
    caption = "Source: Data collected using a Google Form",
    x = "Purpose of phone use",
    y = "Number of sessions"
  )

# To find out what purpose have most increased and decreased productivity
most_increase_df <- latest_data %>%
  filter(productivity == "Increased") %>%
  count(purpose) %>%
  slice_max(n, n = 1)

most_increase <- most_increase_df$purpose

most_decrease_df <- latest_data %>%
  filter(productivity == "Decreased") %>%
  count(purpose) %>%
  slice_max(n, n = 1)

most_decrease <- most_decrease_df$purpose

```

**`r most_increase`**-related phone usage is most associated with increased productivity. 
In contrast, **`r most_decrease`** is most associated with decreased productivity.

---

## The Duration of Phone Sessions Affect on Productivity
```{r}
#Bar chart
latest_data <- latest_data %>%
  mutate(session_group = cut(
    minutes_per_session,
    breaks = c(0, 35, 70, 105, 1000),
    labels = c("0–35", "35–70", "70–105", "105+")
  ))

latest_data %>%
  ggplot(aes(x = session_group, fill = productivity)) +
  geom_bar() +
  labs(
    title = "Does the Duration of Phone Sessions Affect Productivity?",
    subtitle = "Comparing productivity across different session lengths",
    caption = "Source: Data collected using a Google Form",
    x = "Session length (minutes)",
    y = "Number of sessions"
  )

# The average minutes for decreased productivity
avg_decreased <- mean(latest_data$minutes_per_session[latest_data$productivity == "Decreased"])

```

As shown in the bar chart, phone sessions longer than 105 minutes are associated with a higher number of decreased productivity outcomes, while shorter sessions tend to have fewer decreases in productivity.

Phone sessions that resulted in decreased productivity had an average duration of **`r avg_decreased` minutes**.
